Here are clear instructions to help someone understand what your "Healthy Harvest" website is about:

1. Overview:
	- Healthy Harvest is a digital advisory platform designed to support groundnut farmers.
	- The website provides AI-powered tools and expert advice to help farmers improve crop health, manage diseases, and make informed decisions.

2. Key Features:
	- AI Disease Diagnosis: Upload plant images to get instant disease detection and treatment recommendations.
	- Weather Advisory: Access real-time weather forecasts and historical weather data to plan farming activities.
	- Market Analysis: Get AI-driven insights on market trends and prices for groundnut and related crops.
	- Expert Advice: Connect with agricultural experts for personalized guidance.
	- Notifications: Receive timely alerts about weather, pests, diseases, and market changes.
	- Glossary: Learn agricultural terms and best practices.

3. How to Use:
	- Register or log in to access personalized features.
	- Use the dashboard to view farm stats, recent advisories, and alerts.
	- Navigate through the menu to access diagnosis, weather, market, and advice sections.
	- Upload images for disease diagnosis or check the weather and market pages for updates.

4. Who is it for?
	- Farmers, agricultural extension workers, and anyone interested in groundnut farming and smart agriculture.

5. Benefits:
	- Increases productivity and reduces crop loss.
	- Empowers users with timely, data-driven decisions.
	- Connects users with experts and a community of farmers.

This summary can be used as a guide or introduction for new users visiting your website.
